\pkg{cv}: An \proglang{R} Package for Cross-Validating Regression Models

### 2024-05-23 scratch/notes_john/JSS-article/JSS-article-3.tex
version -> 2.0.1; fix typo in notes vignette

Residual standard error: 4.374 on 389 degrees of freedom
Multiple R-squared:  0.6876,    Adjusted R-squared:  0.686 
F-statistic:   428 on 2 and 389 DF,  p-value: < 2.2e-16
\end{CodeOutput}
\begin{CodeInput}
R> cv(m.auto, confint=TRUE)
\end{CodeInput}
\begin{CodeOutput}
R RNG seed set to 423102
\end{CodeOutput}
\begin{CodeOutput}
10-Fold Cross Validation
method: Woodbury
criterion: mse
cross-validation criterion = 19.27853
bias-adjusted cross-validation criterion = 19.26291
95% CI for bias-adjusted CV criterion = (15.80408, 22.72175)
full-sample criterion = 18.98477 
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> BayesRule
\end{CodeInput}
\begin{CodeOutput}
function (y, yhat) 
{
    if (!all(y %in% c(0, 1))) 
        stop("response values not all 0 or 1")
    if (any(yhat < 0) || any(yhat > 1)) 
        stop("fitted values outside of interval [0, 1]")
    yhat <- round(yhat)
    result <- mean(y != yhat)
    attr(result, "casewise loss") <- "y != round(yhat)"
    result
}
<bytecode: 0x12e288c00>
<environment: namespace:cv>
\end{CodeOutput}
\end{CodeChunk}

>>>>

Residual standard error: 4.374 on 389 degrees of freedom
Multiple R-squared:  0.6876,    Adjusted R-squared:  0.686 
F-statistic:   428 on 2 and 389 DF,  p-value: < 2.2e-16
\end{CodeOutput}
\begin{CodeInput}
R> cv(m.auto, confint=TRUE)
\end{CodeInput}
\begin{CodeOutput}
R RNG seed set to 486347
\end{CodeOutput}
\begin{CodeOutput}
10-Fold Cross Validation
method: Woodbury
criterion: mse
cross-validation criterion = 19.52274
bias-adjusted cross-validation criterion = 19.49438
95% CI for bias-adjusted CV criterion = (15.96188, 23.02687)
full-sample criterion = 18.98477 
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> BayesRule
\end{CodeInput}
\begin{CodeOutput}
function(y, yhat) {
  if (!all(y %in% c(0, 1)))
    stop("response values not all 0 or 1")
  if (any(yhat < 0) ||
      any(yhat > 1))
    stop("fitted values outside of interval [0, 1]")
  yhat <- round(yhat)
  result <- mean(y != yhat) # proportion in error
  attr(result, "casewise loss") <- "y != round(yhat)"
  result
}
<bytecode: 0x111a6b780>
<environment: namespace:cv>
\end{CodeOutput}
\end{CodeChunk}
